Modelling BCG vaccination in the UK

### 2019-06-20 rmds/09-model-fitting.Rmd
updating model-fitting data points

In addition to the notification data available via the ETS pulmonary TB notifications (including both UK born and non-UK born cases) from 1990 were also fitted too. These TB notifications made to Statutory Notifications of Infectious Diseases (NOIDS) from 1913 to 1999. These data were sourced from Public Health England,[@PHE2017] and made available in R using `tbinenglanddataclean`^[Historic TB notification data via `tbinenglanddataclean`: https://www.samabbott.co.uk/tbinenglanddataclean/]. Data from 1990 was used as using data from a decade prior to the time period of interest allows the long term trends to be fitted to. Only a single data point was used as this limited the impact on the compute time of the fitting pipeline. Additional data points would have brought only marginal improvements to the model fit (see Section \@ref(particle-filter)).

>>>>

In addition to the notification data available via the ETS pulmonary TB notifications (including both UK born and non-UK born cases) from 1990, 1994, and 1998 were also fitted too. These TB notifications were made to Statutory Notifications of Infectious Diseases (NOIDS) from 1913 to 1999. These data were sourced from Public Health England,[@PHE2017] and made available in R using `tbinenglanddataclean`^[Historic TB notification data via `tbinenglanddataclean`: https://www.samabbott.co.uk/tbinenglanddataclean/]. Data from these time points was used as using data from the decade prior to the time period of interest allows the long term trends to be fitted to. A subset of the available data was used as this limited the impact on the compute time of the fitting pipeline. Additional data points would have brought only marginal improvements to the model fit (see Section \@ref(particle-filter)).
